---
title: "Global TB Report 2018: Headline statistics"
date: "`r format(Sys.time(), '%Y-%m-%d %H:%M')`"
output: 
  html_document:
    theme: null
    highlight: null
    mathjax: null
---

```{r setup, include=FALSE}

# Hide code from chunks by default
knitr::opts_chunk$set(echo = FALSE)

```

## Global notifications, `r report_year - 1`

```{r m_f_ratio}

# Calculate the global male:female ratio
sex_data <- notification %>% 
            filter(year == report_year - 1) %>% 
            select(newrel_m014, newrel_m15plus, newrel_mu, 
                   newrel_f014, newrel_f15plus, newrel_fu) %>% 
            summarise_all(sum, na.rm = TRUE) %>% 
            mutate(m_f_ratio = (newrel_m014 + newrel_m15plus +newrel_mu) / 
                                (newrel_f014 + newrel_f15plus + newrel_fu))

```


* Male:female ratio: `r display_num(sex_data$m_f_ratio)`

```{r pct_kids}

#clear previous junk
rm(sex_data)

# Calculate the global % of children aged 0 -14
age_data <- notification %>% 
            filter(year == report_year - 1) %>% 
            select(newrel_m014, newrel_m15plus,
                   newrel_f014, newrel_f15plus, 
                   newrel_sexunk014, newrel_sexunk15plus) %>% 
            summarise_all(sum, na.rm = TRUE) %>% 
            mutate(pct_kids = (newrel_m014 + newrel_f014) * 100 / 
                                (newrel_m014 + newrel_f014 + newrel_m15plus + newrel_f15plus))

```

* Percentage of children aged 0-14 amongst notified: `r display_num(age_data$pct_kids)`%

```{r pct_hiv}

#clear previous junk
rm(age_data)

# Calculate the global % of cases with known HIV status
hivtest_data <-  TBHIV_for_aggregates %>% 
                  filter(year == report_year - 1| year == report_year - 2) %>% 
                  select(year, hivtest_pct_numerator, hivtest_pct_denominator) %>% 
                  filter(!is.na(hivtest_pct_numerator) & !is.na(hivtest_pct_denominator) ) %>% 
                  group_by(year) %>% 
                  summarise_at(vars(hivtest_pct_numerator, hivtest_pct_denominator),
                               sum, 
                               na.rm = TRUE) %>% 
                  mutate(pct_hivtest = hivtest_pct_numerator * 100 / 
                                        hivtest_pct_denominator)

```




* Percentage of TB cases with documented HIV test result: `r display_num(hivtest_data[hivtest_data$year==report_year - 1,"pct_hivtest"])`%   (in the previous year it was `r display_num(hivtest_data[hivtest_data$year==report_year - 2,"pct_hivtest"])`%)

